True versus apparent shapes of astrophysical bow shocks

### 2017-04-02 papers/Paper1/sec-quadrics-observations.tex
Start write up of A-D tests

A third factor that may influence \(R_0\) is the inclination, \(i\),
of the bow shock axis with respect to the plane of the sky.

@@

>>>>

A third factor that may influence \(R_0\) is the inclination, \(i\),
of the bow shock axis with respect to the plane of the sky.
Figure~\ref{fig:quadric-projection}b shows that for \(R_c > 1\), then
the projected \(R_0'\) becomes larger than the true \(R_0\) as \(|i|\)
increases.  This is further illustrated in
Figure~\ref{fig:projected-R90-Rc-snapshots} for simple quadric shapes
(spheroids, paraboloids, hyperboloids) and in
Figure~\ref{fig:thin-shell-R90-Rc-snapshots} for the carawilkinoids
and ancarawilkinoids.  It can be seen that the effect is relatively
modest for bow shocks with projected shapes falling in the range
\(1 < R_c/R_0 < 3\) and \(R_{90}/R_0 < 3\), as the vast majority of
our observed sources do.  The increase in \(R_0\) is no more than a
factor of 2 to 3 for moderate inclinations of \(30\) to \(60\degr\),
although it can reach a factor of 5 to 10 for some shapes at more
extreme inclinations.

%% Maybe talk about the other correlations later if we have time

@@

We now investigate if the bow shock shapes of the MIPSGAL sources are
correlated with any other parameters via the following methodology:
\begin{enumerate}[1.]
\item For each of the parameters in the \citet{Kobulnicky:2016a}
  catalog, we divide the sources into two or more sub-samples,
  according to the value of the parameter.  For quantitative
  parameters, such as those discussed in the previous section, we use
  two sub-samples of equal size, with membership determined by whether
  the parameter is larger or smaller than the median value.  But we
  also use categorical parameters, such as the type of bow shock
  environment, or the presence/absence of \SI{8}{\um} emission, in
  which case the sub-samples are of unequal size.
\item We plot the KDEs of the two sub-samples separately on the
  \(R_c\)--\(R_{90}\) plane (see Figs.~\ref{fig:mipsgal-correlated} and
  \ref{fig:mipsgal-uncorrelated}) to check for any obvious
  differences.
\item We test if there is any statistically significant difference
  between the shape distributions of the sub-samples by applying the
  2-sample Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a} to the
  \(R_c/R_0\) and \(R_{90}/R_0\) distributions separately.  This is a
  non-parametric test of the \textit{null hypothesis} that the two
  sub-samples are drawn from the same distribution.

\end{enumerate}
